Ordinal Tax To Sustain a Digital Economy

### 2019-08-10 writing/short note on digital tax/DigitalTax.tex
added technical appendix to short note.

The two firms choose capacity and price to maximize their respective profit in equilibrium. 
Here, we assume they first compete on capacity, by simultaneously declaring how many units they produce;
next, they compete on price, taking into consideration the tax and assuming the location of buyers is known. 
This process, consisting of these two dependent sub-games, is similar to the game theoretical problems studied by \cite{Kreps1983}, the major difference being the buyer-seller specific tax.
Quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
%The firm's strategy-space is thus given by the quantity that they can produce and the prices that they can offer. 
Because the tax depends on the exact location of buyers and firms, 
it is not possible to determine the Nash equilibrium analytically, for general cases. 
Instead, we use the Gambit library developed by \cite{McKelvey2016} to find the Nash equilibrium numerically. 
%To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
%The quantity-price two-step game is solved in reverse order: 
%For every choice of quantity, the equilibrium price is determined.
%Then, the equilibrium quantity is determined.

@@

SC Lera acknowledges stimulating discussions with S. Donick.

@@

>>>>

The two firms choose capacity and price to maximize their respective profit in equilibrium. 
Here, we assume they first compete on capacity, by simultaneously declaring how many units they produce;
next, they compete on price, taking into consideration the tax and assuming the location of buyers is known. 
This process, consisting of these two dependent sub-games, is similar to the game theoretical problems studied by \cite{Kreps1983}, the major difference being the buyer-seller specific tax.
Quantity and price offered by each firm are determined as the Nash equilibrium of this two-stage game. 
Because the tax depends on the exact location of buyers and firms, 
it is in general not possible to determine the Nash equilibrium analytically. 
We thus revert to numerical techniques described in \ref{apx:Nash_numerical}.

@@

S. Lera acknowledges stimulating discussions with S. Donick.

@@

\appendix
\section{Numerical Solution of Nash Equilibrium} 
\label{apx:Nash_numerical}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In order to maximise their profit, firms first compete on capacity, by simultaneously declaring how many units they produce.
Subsequently, they compete on price. 
This amounts to a two-step game theoretical problem, whereby quantity and price are determined as the Nash equilibrium. 
Each firm's strategy-space is given by the quantity that they can produce and the prices that they can offer. 
We use the Gambit library developed by \cite{McKelvey2016} to find this equilibrium numerically. 
To this end, the strategy space of capacities and prices are discretised into a sufficiently fine grid. 
The quantity-price two-step game is then solved in reverse order: 
For every choice of quantity, the equilibrium price is determined.
Then, the equilibrium quantity is determined. 
%A detailed description and code is available from the authors upon request.
